A Quasi-Genuine FIFO Total Order Multicast Primitive

### 2011-06-08 trunk/textos/optpaxos/draftv3.tex
relwork, proof, experiments, conclusion

\documentclass[times, 10pt]{article} 
%\documentclass[times, 10pt,twocolumn]{article} 
%\usepackage[noend]{distribalgo}
\usepackage{algorithm}
%\usepackage{times}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{color}
\usepackage{amssymb}
\usepackage[noend]{distribalgo}
\usepackage[draft]{fixme}
\usepackage[hmargin=2cm,vmargin=2cm]{geometry}

@@

\section{Quasi-Genuine FIFO Total Order Multicast}
\label{sec:quasi}

@@

\subsection{Message delivery algorithm}

@@

\subsubsection{Addressing liveness}

@@

>>>>

\documentclass[times, 10pt]{article} 
%\documentclass[times, 10pt,twocolumn]{article} 
%\usepackage[noend]{distribalgo}
\usepackage{algorithm}
%\usepackage{times}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{color}
\usepackage{amssymb}
\usepackage[noend]{distribalgo}
\usepackage[draft]{fixme}
\usepackage[hmargin=2.5cm,vmargin=2.2cm]{geometry}

@@

%\section{Quasi-Genuine FIFO Total Order Multicast}
%\label{sec:quasi}

@@

\section{Message delivery algorithm}

@@

\subsection{Addressing liveness}

@@

\subsection{Optimistic delivery}

\section{Proof of correctness}

\section{Related work}

\cite{sousa2002oto}: optimistic total order bcast in wans: for the opt-delivery to work properly, requires that the delay between each pair of processes stay constant (ours only requires that it never goes beyond $w(p)$ for each process $p$\ldots). sequencer based (no tolerance for failures of the sequencer). not mentioning multicast.

\section{Experimental results}

Really necessary?

\section{Conclusion}
